Lecture 8: Extensive Form Games with Perfect Information

### 2014-11-03 course-game/session1/ehsan_session1.tex
changes

\begin{frame}{Overview}
    \begin{itemize}
     	\itemsep=.5cm
    	\item {\bf Introduction}
    	\item S2
    	\item S3
    	\item S4
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background}
\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item {\bf Background and Literature Review}
    	\item Proposed Research
    	\item Timeline and Feature Work
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame9 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame11 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cooperative Game Theory}

@@

    $\forall C_1,C_2 \subseteq N$
    \begin{itemize}
        \item {\color{blue} Convex:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2) - v(C_1 \bigcap C_2)$. Convexity has important properties in cooperative game theory solution concepts.
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Solution Properties}
    Let $x \in R^n$ be a solution of the coalition game $(N,v)$
    \begin{itemize}
        \item {\color{blue} Feasible solution:} $\sum_{i \in N} x(i) \leq v(N)$
        \item {\color{blue} Efficiency:} $\sum_{i \in N} x(i) = v(N)$
        \begin{itemize}
            \item the payoff distribution is an allocation of the entire worth of the grand coalition to all agents.
        \end{itemize}
        \item {\color{blue} Individual rationality:} $\forall i \in N, x(i) \geq v(\{i\})$
        \begin{itemize}
            \item player obtains at least its self-value of payoff.
        \end{itemize}
        \item {\color{blue} Group rationality:} $\forall C \subseteq N, \sum_{i \in N} x(i) \geq v(C)$
    \end{itemize}

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Stability}
    \begin{itemize}
        \item We all want to work together and get $v(N)$, but we all have different views about how to share the fruits of our work. We can use the values of other coalitions as arguments in favor of a distribution.
        \item A condition for a coalition to form:
            {\color{blue}all} agents prefer to be in it. i.e., none of the participants wishes she were in a different coalition or by herself {\color{blue} $\Rightarrow Stability$ }
        \item The {\color{blue} core} is a stability concept for which no agents prefer to deviate to form a different coalition.
    \end{itemize}
\end{frame}

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Solution Concepts: Shapley Value}
    \begin{definition} [Marginal Contribution]\label{dfn:marginalcontribution}
        The {\color{blue}marginal contribution} of agent $i$ for a coalition $C \subseteq N \backslash \{i\}$ is $mc_i(C) = v(C \cup \{i\}) - v(C)$
    \end{definition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{$\epsilon$-Core}
    \begin{itemize}
        \item The core may not always be non-empty, core is a strong condition.
        \item $\epsilon$-core relaxes the core condition.
        \item $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon$
        \item relative $\epsilon$-Core: $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq (1-\epsilon).v(S)$
    \end{itemize}
\end{frame}

>>>>

\begin{frame}{Overview}
    \begin{itemize}
     	\itemsep=.5cm
    	\item {\bf Coalition Games}
    	\item Stability and Core
    	\item Fairness and Shapley Value
    	\item Other Solution Conecpts
        \item Practical Example
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coalition Games}
\subsection{Cooperative Game Theory}

@@

    $\forall C_1,C_2 \subseteq N$
    \begin{itemize}
        \item {\color{blue} Convex:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2) - v(C_1 \bigcap C_2)$. Convexity has important properties in cooperative game theory solution concepts.
    \end{itemize}

    $\forall C \subseteq S \subseteq N$
    \begin{itemize}
        \item {\color{blue} Monotonic:} $v(C) \leq v(S)$
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Solution Properties}
    Let $x \in R^n$ be a solution of the coalition game $(N,v)$
    \begin{itemize}
        \item {\color{blue} Feasible solution:} $\sum_{i \in N} x(i) \leq v(N)$
        \item {\color{blue} Efficiency:} $\sum_{i \in N} x(i) = v(N)$
        \begin{itemize}
            \item the payoff distribution is an allocation of the entire worth of the grand coalition to all agents.
        \end{itemize}
        \item {\color{blue} Individual rationality:} $\forall i \in N, x(i) \geq v(\{i\})$
        \begin{itemize}
            \item player obtains at least its self-value of payoff.
        \end{itemize}
        \item {\color{blue} Group rationality:} $\forall C \subseteq N, \sum_{i \in N} x(i) \geq v(C)$
        \begin{itemize}
            \item if $\sum_{i \in N} x(i) < v(C)$ is not worth it for some $C$
            \item if $\sum_{i \in N} x(i) > v(C)$ is not possible for all $C$
        \end{itemize}
        \item {\color{blue} Pareto Optimal:} $\sum_{i \in N} x(i) = v(N)$
        \begin{itemize}
            \item no agent can improve its payoff without lowering the payoff of another agent
        \end{itemize}
        \item {\color{blue} Anonymity:} a solution is independent of the names of the player.
    \end{itemize}

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stability and Core}
\subsection{Stability and Core}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Overview}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Coalition Games
    	\item {\bf Stability and Core}
    	\item Fairness and Shapley Value
    	\item Other Solution Conecpts
        \item Practical Example
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Stability}
    \begin{itemize}
        \item We all want to work together and get $v(N)$, but we all have different views about how to share the fruits of our work. We can use the values of other coalitions as arguments in favor of a distribution.
        \item A condition for a coalition to form:
            {\color{blue}all} agents prefer to be in it. i.e., none of the participants wishes she were in a different coalition or by herself {\color{blue} $\Rightarrow Stability$ }
        \item The {\color{blue} core} is a stability concept for which no agents prefer to deviate to form a different coalition.
    \end{itemize}
\end{frame}

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fairness and Shapley Value}
\subsection{Fairness and Shapley Value}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Overview}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Coalition Games
    	\item Stability and Core
    	\item {\bf Fairness and Shapley Value}
    	\item Other Solution Conecpts
        \item Practical Example
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Solution Concepts: Shapley Value}
    \begin{definition} [Marginal Contribution]\label{dfn:marginalcontribution}
        The {\color{blue}marginal contribution} of agent $i$ for a coalition $C \subseteq N \backslash \{i\}$ is $mc_i(C) = v(C \cup \{i\}) - v(C)$
    \end{definition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Other Solution Concepts}
\subsection{Other Solution Concepts}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Overview}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Coalition Games
    	\item Stability and Core
    	\item Fairness and Shapley Value
    	\item {\bf Other Solution Conecpts}
        \item Practical Example
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{$\epsilon$-Core}
    \begin{itemize}
        \item The core may not always be non-empty, core is a strong condition.
        \item $\epsilon$-core relaxes the core condition.
        \item $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon$
        \item relative $\epsilon$-Core: $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq (1-\epsilon).v(S)$
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Excess of a coalition}
    \begin{itemize}
        \item We consider one way to compare two imputations.
    \end{itemize}

    \begin{definition} [Excess of a coalition]\label{dfn:marginalcontribution}
        Let (N,v) be a $TU$ game, $C \subseteq N$ be a coalition, and $x$ be a payoff distribution over $N$. The excess $e(C,x)$ of coalition $C$ at $x$ is the quantity $e(C,x) = v(C) - x(C)$.
    \end{definition}

    \begin{itemize}
        \item Example: 
        \begin{itemize}
            \item let $N={1,2,3}, C={1,2}, v({1,2})=8, x=(3,2,5)$
            \item $e(C,x)=v({1,2})-(x_1 + x_2)=8-(3+2)=3.$
        \end{itemize}
        \item We can interpret a positive excess $(e(C,x) > 0)$ as the amount of dissatisfaction or {\color{blue} complaint} of the members of $C$ from the allocation x.
        \item We can use the excess to define the core:
        \begin{itemize}
            \item $Core(N,v)=\{x \in R^n | x is an imputation and \forall C \subseteq N, e(C,x) \leq 0\}$
        \end{itemize}
        \item This definition shows that no coalition has any complaint: each coalition's demand can be granted.
    \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Excess of a coalition: Example}

    \centerline{$N = {1,2,3}$, $v(\{i\})=0$ $for$ $i \in \{1,2,3\}$ $v(\{1,2\}) = 5$}
    \centerline{$v(\{1,3\}) = 6$, $v(\{2,3\}) = 6$, $v(N) = 8$}

     \begin{itemize}
        \item Let us consider two payoff vectors $x = \{3, 3,2\}$ and $y = \{2, 3,3\}$.
        \item Let $e(x)$ denote the sequence of excesses of all coalitions at $x$.
     \end{itemize}

     \begin{table}[!htb]
        \begin{minipage}{.5\linewidth}
          \centering
            \begin{tabular}{c|c}                
                \multicolumn{2}{c}{x = \{3,3,2\}} \\
                \hline
                \emph{Coalition C} & $e(C,x)$\\
                \hline
                \{1\} & -3\\
                \{2\} & -3\\
                \{3\} & -3\\
                \{1,2\} & -1\\
                \{1,3\} & 1\\
                \{2,3\} & 1\\
                \{1,2,3\} & 0\\
            \end{tabular}
        \end{minipage}%
        \begin{minipage}{.5\linewidth}
          \centering            
            \begin{tabular}{c|c}                
                \multicolumn{2}{c}{x = \{2,3,3\}} \\            
                \hline
                \emph{Coalition C} & $e(C,x)$\\
                \hline
                \{1\} & -2\\
                \{2\} & -3\\
                \{3\} & -3\\
                \{1,2\} & 0\\
                \{1,3\} & 1\\
                \{2,3\} & 0\\
                \{1,2,3\} & 0\\
            \end{tabular}
        \end{minipage}
    \end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Excess of a coalition}
    \begin{itemize}
        \item Which payoff should we prefer? $x$ or $y$? 
        \item Let us write the excess in the decreasing order (from the greatest excess to the smallest)
        \begin{itemize}
            \item $Sorted$ $e(C,x):$ $\{1, 1, 0,-1,-2,-3,-3\}$
            \item $Sorted$ $e(C,y):$ $\{1, 0, 0, 0,-2,-3,-3\}$
        \end{itemize}
    \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Excess of a coalition: lexicographical order}

    \begin{definition} [lexicographical order $\geq_{lex}$]\label{dfn:lexorder}
        Let $\geq_{lex}$ denote the lexicographical ordering of $R^m$, 
        $\forall(x,y) \in R^m, x \geq y$ $iff$ 
        \begin{itemize}
            \item $x=y$ or
            \item $\exists t$ $1 \leq t \leq m$ and $\forall i$ $1 \leq i < t$ $x_i = y_i$ and $x_t > y_t$
        \end{itemize}
    \end{definition}

    \begin{itemize}
        \item Example:
        \begin{itemize}
            \item let $\{1, 1, 0,-1,-2,-3,-3\} \geq_{lex} \{1, 0, 0, 0,-2,-3,-3\}$            
        \end{itemize}        
        \item Let $l$ be a sequence of $m$ reals. We denote by {\color{blue} $l^*$} the {\color{blue} reordering} of {\color{blue} $l$} in {\color{blue} decreasing} order.
        \item In the example, $e(x) = \{3,-3,-2,-1, 1, 1,0\}$ and then $e(x)^* = \{1, 1, 0,-1,-2,-3,-3\}$.
        \item Hence, we can say that $y$ is better than $x$ by writing $e(x)^* \geq e(y)^*$
    \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Nucleolus}
    \begin{itemize}
        \item Let $(N,v)$ be a $TU$ game.
        \item Let $Imp$ be the set of all imputations.
        \item The {\color{blue}$nucleolus Nu(N,v)$} is the set
        \begin{itemize}
            \item $Nu(N,v) = \{x \in Imp|\forall y \in Imp e(y)* \geq_{lex} e(x)*\}$
        \end{itemize}
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Practical Example}
\subsection{Problem Formulation and Modeling}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Overview}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Coalition Games
    	\item Stability and Core
    	\item Fairness and Shapley Value
    	\item Other Solution Conecpts
        \item {\bf Practical Example}
    \end{itemize}
\end{frame}

\begin{frame}{Problem Formulation and Modeling}
    \begin{itemize}
        \item Communities of web services are robust service providers with well established market share and reputation.
        \item The community is characterized by a request rate $R_C$.
        \item Web services can perform tasks with some throughput rate ($Th_{ws}$).
        \item Web services come with different values of $QoS_{ws}$ for different metrics.
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Task Distribution}
    \begin{itemize}
        \item Our model uses a slightly modified \emph{weighted fair queuing} method for task distribution rather than Contract-Net.
        \item All the input flow is multiplexed among different web services with weights proportional to their throughput value ($Th_{ws}$).
        \item Queues will happen if $R_C$ is more than the summation of web services throughput.
        \item Weighted task rate: $R_C \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ or $Th_{ws}$
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.8 \columnwidth]{figures/community.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Community Revenue}
    \begin{itemize}
        \item Maximum potential output of a community:
            \begin{equation*}
                PO(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
            \end{equation*}
        \item if $\sum_{ws}{Th_{ws}} > R_C$, the community cannot perform at its maximum potential.
        \item Actual output:
            \begin{equation}\label{out_c}
                Out(C) = \left\{
                  \begin{array}{l l}
                    PO(C) & \quad \text{if $\sum_{ws}{Th_{ws}} \leq R_{C}$}\\
                    PO(C) \times \frac{R_{C}}{\sum_{ws}{Th_{ws}}} & \quad \text{if $\sum_{ws}{Th_{ws}} > R_{C}$}
                  \end{array} \right.
            \end{equation}
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Example 1}
    \begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    % if using array.sty, it might be a good idea to tweak the value of
    % \extrarowheight as needed to properly center the text within the cells
    \label{example_1}
    \centering
    \begin{tabular}{c c c c}
    \hline
    $WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
    \hline
    1 & 0.8 & 4 & 3.2\\
    2 & 0.8 & 5 & 4.0\\
    3 & 0.8 & 3 & 2.4\\
    \hline
    \end{tabular}
    \end{table}

    \begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    % if using array.sty, it might be a good idea to tweak the value of
    % \extrarowheight as needed to properly center the text within the cells
    % \caption{Three web services}
    \label{example_1_2}
    \centering
    \begin{tabular}{c c || c c}
    \hline
    Community & Worth & Community & Worth\\
    \hline
    $\left\{1\right\}$ & 3.2 & $\left\{1,2\right\}$ & 7.2\\
    $\left\{2\right\}$ & 4.0 & $\left\{1,3\right\}$ & 5.6\\
    $\left\{3\right\}$ & 2.4 & $\left\{2,3\right\}$ & 6.4\\
    $\left\{1,2,3\right\}$ & 8.0\\
    \hline
    Community $R_C$: 10\\
    \hline
    \end{tabular}
    \end{table}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{frame}{Example 2}
%    \begin{table}[!t]
%    \renewcommand{\arraystretch}{1.3}
%    % if using array.sty, it might be a good idea to tweak the value of
%    % \extrarowheight as needed to properly center the text within the cells
%    \label{example_2}
%    \centering
%    \begin{tabular}{c c c c}
%    \hline
%    $WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
%    \hline
%    1 & 0.8 & 5 & 4.0\\
%    2 & 0.7 & 6 & 4.2\\
%    3 & 0.7 & 4 & 2.8\\
%    \hline
%    \end{tabular}
%    \end{table}
%
%    \begin{table}[!t]
%    \renewcommand{\arraystretch}{1.3}
%    % if using array.sty, it might be a good idea to tweak the value of
%    % \extrarowheight as needed to properly center the text within the cells
%    % \caption{Three web services}
%    \label{example_2_2}
%    \centering
%    \begin{tabular}{c c || c c}
%    \hline
%    Community & Worth & Community & Worth\\
%    \hline
%    $\left\{1\right\}$ & 4.0 & $\left\{1,2\right\}$ & 7.4\\
%    $\left\{2\right\}$ & 4.2 & $\left\{1,3\right\}$ & 6.8\\
%    $\left\{3\right\}$ & 2.8 & $\left\{2,3\right\}$ & 7.0\\
%    $\left\{1,2,3\right\}$ & 7.3\\
%    \hline
%    Community $R_C$: 10\\
%    \hline
%    \end{tabular}
%    \end{table}
%\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Example 2}
    \begin{table}[!t]
    \renewcommand{\arraystretch}{0.8}
    % if using array.sty, it might be a good idea to tweak the value of
    % \extrarowheight as needed to properly center the text within the cells
    \label{example_3}
    \centering
    \begin{tabular}{c c c c}
    \hline
    $WS$ & $QoS_{ws}$ & $Th_{ws}$ & $\text{\emph{Input Task Rate}}$\\
    \hline
    1 & 0.8 & 10 & 5\\
    2 & 0.8 & 20 & 5\\
    3 & 0.8 & 30 & 5\\
    \hline
    \end{tabular}
    \end{table}

    \begin{table}[!t]
    \renewcommand{\arraystretch}{0.8}
    % if using array.sty, it might be a good idea to tweak the value of
    % \extrarowheight as needed to properly center the text within the cells
    % \caption{Three web services}
    \label{example_3_2}
    \centering
    \begin{tabular}{c c || c c}
    \hline
    Community & Worth & Community & Worth\\
    \hline
    $\left\{C_{ms_1}\right\}$ & 0 & $\left\{C_{ms_2}\right\}$ & 0\\
    $\left\{C_{ms_1}, ws_1\right\}$ & 8 & $\left\{C_{ms_2}, ws_1\right\}$ & 8\\
    $\left\{C_{ms_1}, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_2\right\}$ & 16\\
    $\left\{C_{ms_1}, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_3\right\}$ & 24\\
    $\left\{C_{ms_1}, ws_1, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2\right\}$ & 24\\
    $\left\{C_{ms_1}, ws_1, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_3\right\}$ & 32\\
    $\left\{C_{ms_1}, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_2, ws_3\right\}$ & 32\\
    $\left\{C_{ms_1}, ws_1, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2, ws_3\right\}$ & 32\\
    $\left\{C_{ms_1}, C_{ms_2}, ...\right\}$ & 0 & $\left\{ws_1\right\}$ & 6.8\\
    $\left\{ws_2\right\}$ & 4.2 & $\left\{ws_3\right\}$ & 6.8\\
    \hline
    Community $R_{C_1}$: 20 \\ Community $R_{C_2}$: 40\\
    \hline
    \end{tabular}
    \end{table}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame19 Proposed Research
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Web Service Cooperative Games}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Community and Web Service Interaction Model - (Phase 1)}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.8 \columnwidth]{figures/scenario1.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}

    \begin{itemize}
        \item A typical WS community, where web services can join or leave.
        \item $v(C) = Out(C)$.
        \item Membership decision in made based on throughput and QoS of the web services.
        \item Community master needs to get quality web services to keep the community stable, so other web services have no incentive to leave.
    \end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Community and Web Service Interaction Model - (Phase 1)}

    \begin{itemize}
        \item Upon receiving membership request, the master web service checks if the coalition will be stable having the new member.
        \item If the game is convex, core exists.
        \item If the game is convex, Shapley value is in core.
        \item Convexity Condition:
        \begin{center}
          $v(A \cup B) \geq v(A) + v(B) - v(A \cap B)$ \\
          $\Leftrightarrow$  \\
          $\forall S,T | S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N,$ \\
          {\color{blue} $v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)$ }
        \end{center}
        \item Depth-1 Convexity Check: $O(n)$
        \item Depth-2 Convexity Check: $O(n^2)$
    \end{itemize}
